### 2017-02-16 thesis/results/results2.tex
tmp commit

>>>>

\begin{table}[htpb]
	\centering
	\caption{caption}
	\label{tab:lm_sig_var}
	\begin{tabular}{llcc}
		Linear Model & Variables & Estimate & P-value\\
		\hline
		\gls{\gls{bmi}}-only                                 & \gls{bmi}  & -0.001481 & 0.717      \\
		\gls{\gls{bmi}} status-only                          & Obese      & -0.09809  & 0.166      \\
                                                             & Overweight & -0.01263  & 0.871      \\
		\gls{\gls{bmi}} and \gls{\gls{bmi}} status           & \gls{bmi}  & 0.01087   & 0.1232     \\
                                                             & Obese      & -0.24812  & 0.0398 *   \\
                                                             & Overweight & -0.06873  & 0.4199     \\
		Pathways only                                        & \gls{bcat} & 0.091552  & 0.6765     \\
                                                             & \gls{er}   & 0.052266  & 0.8342     \\
                                                             & \gls{ifna} & -0.499303 & 0.3070     \\
                                                             & \gls{ifny} & 0.422406  & 0.3983     \\
                                                             & myc        & -0.003752 & 0.9867     \\
                                                             & \gls{pr}   & 0.583569  & 0.0164   * \\
		\gls{\gls{bmi}} and Pathways                         & \gls{bmi}  & -0.002368 & 0.5271     \\
                                                             & \gls{bcat} & 0.112118  & 0.6144     \\
                                                             & \gls{er}   & 0.054001  & 0.8294     \\
                                                             & \gls{ifna} & -0.538290 & 0.2763     \\
                                                             & \gls{ifny} & 0.466144  & 0.3576     \\
                                                             & myc        & 0.016832  & 0.9411     \\
                                                             & \gls{pr}   & 0.592696  & 0.0154   * \\
		\gls{\gls{bmi}} and Pathways                         & Obese      & -0.10346  & 0.1125     \\
                                                             & Overweight & -0.01200  & 0.8641     \\
                                                             & \gls{bcat} & 0.14950   & 0.5008     \\
                                                             & \gls{er}   & 0.03263   & 0.8955     \\
                                                             & \gls{ifna} & -0.67067  & 0.1767     \\
                                                             & \gls{ifny} & 0.58879   & 0.2453     \\
                                                             & myc        & 0.04388   & 0.8457     \\
                                                             & \gls{pr}   & 0.57993   & 0.0164   * \\
		\gls{\gls{bmi}}, \gls{\gls{bmi}} status and pathways & \gls{bmi}  & 0.009057  & 0.1614     \\
                                                             & Obese      & -0.229223 & 0.0397   * \\
                                                             & Overweight & -0.057586 & 0.4546     \\
                                                             & \gls{bcat} & 0.145953  & 0.5087     \\
                                                             & \gls{er}   & 0.009057  & 0.9708     \\
                                                             & \gls{ifna} & -0.693675 & 0.1605     \\
                                                             & \gls{ifny} & 0.588958  & 0.2426     \\
                                                             & myc        & 0.026253  & 0.9070     \\
                                                             & \gls{pr}   & 0.544864  & 0.0240   * \\

% [1] "rawobsgene"

% Call:
% lm(formula = as.formula(formula_txt[j]), data = data)

% Coefficients:
%              Estimate Pr(>|t|)
% [1] "crolgene"

% Call:
% lm(formula = as.formula(formula_txt[j]), data = data)

% Coefficients:
%              Estimate Std. Error t value Pr(>|t|)
% (Intercept)         0.553214  0.123891 4.465  2.16e-05 ***
% bmi                 -0.001629 0.004071 -0.400 0.69
% (Intercept)         0.55700   0.05464  10.194 <2e-16   ***
% bmiStatusobese      -0.10551  0.07021  -1.503 0.136
% bmiStatusoverweight -0.02165  0.07727  -0.280 0.780
% (Intercept)         0.307513  0.163530 1.880  0.0631   .
% bmi                 0.011279  0.006976 1.617  0.1092
% bmiStatusobese      -0.261145 0.118795 -2.198 0.0304   *
% bmiStatusoverweight -0.079845 0.084661 -0.943 0.3480
% (Intercept)         0.007141  0.382725 0.019  0.9852
% bcat_probes         0.156062  0.223779 0.697  0.4873
% er_probes           0.123403  0.254800 0.484  0.6293
% ifna_probes         -0.430229 0.497301 -0.865 0.3892
% ifng_probes         0.378437  0.509352 0.743  0.4594
% myc_probes          0.160785  0.229142 0.702  0.4846
% pr_probes           0.597403  0.244252 2.446  0.0164   *
% (Intercept)         0.055088  0.389472 0.141  0.8878
% bmi                 -0.002745 0.003814 -0.720 0.4736
% bcat_probes         0.179900  0.226799 0.793  0.4297
% er_probes           0.125413  0.255485 0.491  0.6247
% ifna_probes         -0.475417 0.502546 -0.946 0.3466
% ifng_probes         0.429131  0.515526 0.832  0.4074
% myc_probes          0.184642  0.232124 0.795  0.4284
% pr_probes           0.607982  0.245336 2.478  0.0151   *
% (Intercept)         0.01666   0.37989  0.044  0.9651
% bmiStatusobese      -0.11197  0.06602  -1.696 0.0933   .
% bmiStatusoverweight -0.02348  0.07151  -0.328 0.7434
% bcat_probes         0.22035   0.22616  0.974  0.3325
% er_probes           0.10450   0.25330  0.413  0.6809
% ifna_probes         -0.60343  0.50372  -1.198 0.2341
% ifng_probes         0.54671   0.51484  1.062  0.2911
% myc_probes          0.21341   0.22998  0.928  0.3559
% pr_probes           0.59491   0.24257  2.453  0.0161   *
% (Intercept)         -0.128149 0.393204 -0.326 0.7453
% bmi                 0.008834  0.006565 1.346  0.1819
% bmiStatusobese      -0.234634 0.112386 -2.088 0.0397   *
% bmiStatusoverweight -0.067942 0.078484 -0.866 0.3890
% bcat_probes         0.216892  0.225167 0.963  0.3380
% er_probes           0.081506  0.252745 0.322  0.7478
% ifna_probes         -0.625864 0.501740 -1.247 0.2155
% ifng_probes         0.546873  0.512538 1.067  0.2889
% myc_probes          0.196215  0.229305 0.856  0.3945
% pr_probes           0.560706  0.242816 2.309  0.0232   *

% [1] "resobsgene"

% Call:
% lm(formula = as.formula(formula_txt[j]), data = data)

% Coefficients:
%              Estimate Std. Error t value Pr(>|t|)
% (Intercept)         0.547104  0.123915 4.415  2.62e-05 ***
% bmi                 -0.001422 0.004072 -0.349 0.728
% (Intercept)         0.547619  0.054641 10.022 <2e-16   ***
% bmiStatusobese      -0.096832 0.070212 -1.379 0.171
% bmiStatusoverweight -0.001804 0.077273 -0.023 0.981
% (Intercept)         0.298589  0.163546 1.826  0.0710   .
% bmi                 0.011259  0.006976 1.614  0.1099
% bmiStatusobese      -0.252186 0.118807 -2.123 0.0364   *
% bmiStatusoverweight -0.059898 0.084669 -0.707 0.4810
% (Intercept)         0.18694   0.36963  0.506  0.6142
% bcat_probes         0.09717   0.21612  0.450  0.6541
% er_probes           0.07879   0.24608  0.320  0.7496
% ifna_probes         -0.17576  0.48029  -0.366 0.7152
% ifng_probes         0.07930   0.49193  0.161  0.8723
% myc_probes          -0.04517  0.22130  -0.204 0.8387
% pr_probes           0.59554   0.23590  2.525  0.0133   *
% (Intercept)         0.221757  0.376612 0.589  0.5574
% bmi                 -0.001994 0.003688 -0.540 0.5902
% bcat_probes         0.114479  0.219311 0.522  0.6029
% er_probes           0.080247  0.247050 0.325  0.7461
% ifna_probes         -0.208580 0.485954 -0.429 0.6688
% ifng_probes         0.116119  0.498505 0.233  0.8163
% myc_probes          -0.027845 0.224460 -0.124 0.9015
% pr_probes           0.603222  0.237235 2.543  0.0127   *
% (Intercept)         0.195965  0.367384 0.533  0.5951
% bmiStatusobese      -0.096834 0.063844 -1.517 0.1328
% bmiStatusoverweight -0.004412 0.069155 -0.064 0.9493
% bcat_probes         0.150379  0.218719 0.688  0.4935
% er_probes           0.058880  0.244961 0.240  0.8106
% ifna_probes         -0.344126 0.487134 -0.706 0.4817
% ifng_probes         0.242697  0.497893 0.487  0.6271
% myc_probes          -0.001285 0.222407 -0.006 0.9954
% pr_probes           0.591191  0.234582 2.520  0.0135   *
% (Intercept)         0.041459  0.379420 0.109  0.9132
% bmi                 0.009426  0.006335 1.488  0.1403
% bmiStatusobese      -0.227717 0.108446 -2.100 0.0386   *
% bmiStatusoverweight -0.051853 0.075733 -0.685 0.4953
% bcat_probes         0.146687  0.217273 0.675  0.5013
% er_probes           0.034350  0.243884 0.141  0.8883
% ifna_probes         -0.368065 0.484150 -0.760 0.4491
% ifng_probes         0.242870  0.494570 0.491  0.6246
% myc_probes          -0.019634 0.221267 -0.089 0.9295
% pr_probes           0.554701  0.234304 2.367  0.0201   *

% [1] "rescrolgene"

% Call:
% lm(formula = as.formula(formula_txt[j]), data = data)

% Coefficients:
%               Estimate Std. Error t value Pr(>|t|)
% (Intercept)         0.5343899  0.1239554 4.311  3.9e-05 ***
% bmi                 -0.0009922 0.0040730 -0.244 0.808
% (Intercept)         0.54870    0.05482   10.009 <2e-16  ***
% bmiStatusobese      -0.09063   0.07044   -1.287 0.201
% bmiStatusoverweight -0.01515   0.07753   -0.195 0.845
% (Intercept)         0.304200   0.164179  1.853  0.0670  .
% bmi                 0.011054   0.007003  1.578  0.1178
% bmiStatusobese      -0.243160  0.119267  -2.039 0.0442  *
% bmiStatusoverweight -0.072189  0.084997  -0.849 0.3978
% (Intercept)         0.17069    0.37929   0.450  0.6537
% bcat_probes         0.09532    0.22177   0.430  0.6683
% er_probes           0.03171    0.25251   0.126  0.9004
% ifna_probes         -0.57965   0.49283   -1.176 0.2426
% ifng_probes         0.50919    0.50478   1.009  0.3157
% myc_probes          0.06345    0.22708   0.279  0.7805
% pr_probes           0.54200    0.24206   2.239  0.0276  *
% (Intercept)         0.204758   0.386507  0.530  0.5976
% bmi                 -0.001950  0.003785  -0.515 0.6076
% bcat_probes         0.112257   0.225072  0.499  0.6192
% er_probes           0.033134   0.253540  0.131  0.8963
% ifna_probes         -0.611750  0.498720  -1.227 0.2231
% ifng_probes         0.545210   0.511601  1.066  0.2894
% myc_probes          0.080405   0.230357  0.349  0.7279
% pr_probes           0.549516   0.243468  2.257  0.0264  *
% (Intercept)         0.17933    0.37777   0.475  0.636
% bmiStatusobese      -0.09681   0.06565   -1.475 0.144
% bmiStatusoverweight -0.01219   0.07111   -0.171 0.864
% bcat_probes         0.14969    0.22490   0.666  0.507
% er_probes           0.01354    0.25189   0.054  0.957
% ifna_probes         -0.73888   0.50091   -1.475 0.144
% ifng_probes         0.66381    0.51197   1.297  0.198
% myc_probes          0.10813    0.22869   0.473  0.638
% pr_probes           0.53872    0.24121   2.233  0.028   *
% (Intercept)         0.027729   0.390580  0.071  0.9436
% bmi                 0.009248   0.006522  1.418  0.1596
% bmiStatusobese      -0.225233  0.111636  -2.018 0.0466  *
% bmiStatusoverweight -0.058734  0.077961  -0.753 0.4532
% bcat_probes         0.146066   0.223664  0.653  0.5154
% er_probes           -0.010526  0.251058  -0.042 0.9667
% ifna_probes         -0.762373  0.498391  -1.530 0.1296
% ifng_probes         0.663981   0.509117  1.304  0.1955
% myc_probes          0.090122   0.227775  0.396  0.6933
% pr_probes           0.502919   0.241196  2.085  0.0399  *

% [1] "caobsgene"

% Call:
% lm(formula = as.formula(formula_txt[j]), data = data)

% Coefficients:
%              Estimate Std. Error t value Pr(>|t|)
% (Intercept)         0.538968  0.123943 4.349  3.39e-05 ***
% bmi                 -0.001147 0.004073 -0.282 0.779
% (Intercept)         0.53896   0.05458  9.875  2.76e-16 ***
% bmiStatusobese      -0.08982  0.07013  -1.281 0.203
% bmiStatusoverweight 0.01804   0.07719  0.234  0.816
% (Intercept)         0.27986   0.16317  1.715  0.0896   .
% bmi                 0.01171   0.00696  1.683  0.0957   .
% bmiStatusobese      -0.25146  0.11853  -2.121 0.0365   *
% bmiStatusoverweight -0.04241  0.08447  -0.502 0.6168
% (Intercept)         0.12454   0.38803  0.321  0.7490
% bcat_probes         0.14068   0.22688  0.620  0.5367
% er_probes           0.11597   0.25833  0.449  0.6545
% ifna_probes         -0.33319  0.50420  -0.661 0.5104
% ifng_probes         0.30871   0.51641  0.598  0.5515
% myc_probes          -0.04569  0.23232  -0.197 0.8445
% pr_probes           0.56692   0.24764  2.289  0.0243   *
% (Intercept)         0.162063  0.395326 0.410  0.6828
% bmi                 -0.002148 0.003872 -0.555 0.5804
% bcat_probes         0.159335  0.230208 0.692  0.4906
% er_probes           0.117547  0.259326 0.453  0.6514
% ifna_probes         -0.368552 0.510101 -0.723 0.4718
% ifng_probes         0.348376  0.523276 0.666  0.5072
% myc_probes          -0.027017 0.235613 -0.115 0.9090
% pr_probes           0.575201  0.249024 2.310  0.0232   *
% (Intercept)         0.134514  0.384960 0.349  0.7276
% bmiStatusobese      -0.099695 0.066899 -1.490 0.1397
% bmiStatusoverweight 0.008987  0.072463 0.124  0.9016
% bcat_probes         0.193430  0.229183 0.844  0.4009
% er_probes           0.092451  0.256681 0.360  0.7196
% ifna_probes         -0.522336 0.510440 -1.023 0.3089
% ifng_probes         0.492130  0.521713 0.943  0.3481
% myc_probes          -0.001892 0.233048 -0.008 0.9935
% pr_probes           0.560583  0.245805 2.281  0.0249   *
% (Intercept)         -0.028482 0.397505 -0.072 0.9430
% bmi                 0.009944  0.006637 1.498  0.1376
% bmiStatusobese      -0.237770 0.113616 -2.093 0.0392   *
% bmiStatusoverweight -0.041061 0.079343 -0.518 0.6061
% bcat_probes         0.189535  0.227630 0.833  0.4073
% er_probes           0.066573  0.255509 0.261  0.7950
% ifna_probes         -0.547591 0.507227 -1.080 0.2832
% ifng_probes         0.492312  0.518143 0.950  0.3446
% myc_probes          -0.021250 0.231813 -0.092 0.9272
% pr_probes           0.522087  0.245472 2.127  0.0362   *

% [1] "cacrolgene"

% Call:
% lm(formula = as.formula(formula_txt[j]), data = data)

% Coefficients:
%               Estimate Std. Error t value Pr(>|t|)
% (Intercept)         5.062e-01  1.240e-01 4.083  9.16e-05 ***
% bmi                 -3.953e-05 4.074e-03 -0.010 0.992
% (Intercept)         0.52453    0.05485   9.564  1.29e-15 ***
% bmiStatusobese      -0.06411   0.07047   -0.910 0.365
% bmiStatusoverweight 0.02958    0.07756   0.381  0.704
% (Intercept)         0.273274   0.164135  1.665  0.0992   .
% bmi                 0.011360   0.007001  1.622  0.1080
% bmiStatusobese      -0.220856  0.119235  -1.852 0.0671   .
% bmiStatusoverweight -0.029032  0.084974  -0.342 0.7334
% (Intercept)         0.02932    0.40048   0.073  0.9418
% bcat_probes         0.23660    0.23416   1.010  0.3150
% er_probes           0.09521    0.26662   0.357  0.7218
% ifna_probes         -0.49129   0.52037   -0.944 0.3476
% ifng_probes         0.44466    0.53298   0.834  0.4063
% myc_probes          0.16111    0.23977   0.672  0.5033
% pr_probes           0.49566    0.25558   1.939  0.0555   .
% (Intercept)         0.051698   0.408467  0.127  0.8996
% bmi                 -0.001281  0.004000  -0.320 0.7495
% bcat_probes         0.247720   0.237861  1.041  0.3004
% er_probes           0.096149   0.267946  0.359  0.7205
% ifna_probes         -0.512383  0.527057  -0.972 0.3335
% ifng_probes         0.468320   0.540670  0.866  0.3887
% myc_probes          0.172240   0.243445  0.708  0.4811
% pr_probes           0.500601   0.257301  1.946  0.0548   .
% (Intercept)         0.03806    0.39931   0.095  0.9243
% bmiStatusobese      -0.07973   0.06939   -1.149 0.2536
% bmiStatusoverweight 0.02249    0.07516   0.299  0.7655
% bcat_probes         0.27648    0.23772   1.163  0.2479
% er_probes           0.07298    0.26625   0.274  0.7846
% ifna_probes         -0.66043   0.52946   -1.247 0.2155
% ifng_probes         0.60854    0.54116   1.125  0.2638
% myc_probes          0.19456    0.24173   0.805  0.4230
% pr_probes           0.48849    0.25497   1.916  0.0586   .
% (Intercept)         -0.123986  0.412743  -0.300 0.7646
% bmi                 0.009886   0.006892  1.434  0.1549
% bmiStatusobese      -0.216997  0.117971  -1.839 0.0692   .
% bmiStatusoverweight -0.027267  0.082384  -0.331 0.7414
% bcat_probes         0.272606   0.236356  1.153  0.2518
% er_probes           0.047249   0.265304  0.178  0.8591
% ifna_probes         -0.685542  0.526672  -1.302 0.1964
% ifng_probes         0.608724   0.538006  1.131  0.2609
% myc_probes          0.175314   0.240700  0.728  0.4683
% pr_probes           0.450215   0.254882  1.766  0.0808   .

% [1] "caresobsgene"

% Call:
% lm(formula = as.formula(formula_txt[j]), data = data)

% Coefficients:
%             Estimate Std. Error t value Pr(>|t|)
% (Intercept)         0.462424  0.123913 3.732  0.00032  ***
% bmi                 0.001442  0.004072 0.354  0.72408
% (Intercept)         0.46970   0.05452  8.616  1.39e-13 ***
% bmiStatusobese      0.09338   0.07005  1.333  0.186
% bmiStatusoverweight -0.01840  0.07710  -0.239 0.812
% (Intercept)         0.722057  0.163100 4.427  2.55e-05 ***
% bmi                 -0.011409 0.006957 -1.640 0.1043
% bmiStatusobese      0.250806  0.118483 2.117  0.0369   *
% bmiStatusoverweight 0.040473  0.084438 0.479  0.6328
% (Intercept)         1.1017    0.3815   2.888  0.00483  **
% bcat_probes         -0.2217   0.2230   -0.994 0.32284
% er_probes           -0.2308   0.2540   -0.909 0.36579
% ifna_probes         0.1853    0.4957   0.374  0.70938
% ifng_probes         -0.1528   0.5077   -0.301 0.76408
% myc_probes          -0.0737   0.2284   -0.323 0.74765
% pr_probes           -0.6876   0.2434   -2.825 0.00581  **
% (Intercept)         1.056654  0.388317 2.721  0.00780  **
% bmi                 0.002580  0.003803 0.678  0.49929
% bcat_probes         -0.244104 0.226127 -1.079 0.28322
% er_probes           -0.232713 0.254728 -0.914 0.36335
% ifna_probes         0.227770  0.501056 0.455  0.65049
% ifng_probes         -0.200460 0.513998 -0.390 0.69745
% myc_probes          -0.096122 0.231435 -0.415 0.67888
% pr_probes           -0.697585 0.244608 -2.852 0.00538  **
% (Intercept)         1.09174   0.37821  2.887  0.00488  **
% bmiStatusobese      0.10153   0.06573  1.545  0.12592
% bmiStatusoverweight -0.00544  0.07119  -0.076 0.93926
% bcat_probes         -0.27598  0.22517  -1.226 0.22351
% er_probes           -0.20770  0.25218  -0.824 0.41234
% ifna_probes         0.37360   0.50149  0.745  0.45823
% ifng_probes         -0.33545  0.51257  -0.654 0.51449
% myc_probes          -0.11868  0.22896  -0.518 0.60548
% pr_probes           -0.68170  0.24150  -2.823 0.00586  **
% (Intercept)         1.235747  0.391476 3.157  0.00218  **
% bmi                 -0.008785 0.006537 -1.344 0.18237
% bmiStatusobese      0.223518  0.111892 1.998  0.04881  *
% bmiStatusoverweight 0.038776  0.078139 0.496  0.62094
% bcat_probes         -0.272540 0.224177 -1.216 0.22730
% er_probes           -0.184837 0.251634 -0.735 0.46455
% ifna_probes         0.395907  0.499535 0.793  0.43015
% ifng_probes         -0.335611 0.510285 -0.658 0.51243
% myc_probes          -0.101582 0.228298 -0.445 0.65743
% pr_probes           -0.647688 0.241749 -2.679 0.00879  **

% [1] "carescrolgene"

% Call:
% lm(formula = as.formula(formula_txt[j]), data = data)

% Coefficients:
%              Estimate Std. Error t value Pr(>|t|)
% (Intercept)         0.4928357 0.1239867 3.975  0.000136 ***
% bmi                 0.0004131 0.0040740 0.101  0.919450
% (Intercept)         0.52814   0.05483   9.633  9.13e-16 ***
% bmiStatusobese      -0.06913  0.07045   -0.981 0.329
% bmiStatusoverweight 0.02453   0.07753   0.316  0.752
% (Intercept)         0.232845  0.163204  1.427  0.1569
% bmi                 0.013351  0.006962  1.918  0.0582   .
% bmiStatusobese      -0.253344 0.118558  -2.137 0.0352   *
% bmiStatusoverweight -0.044356 0.084492  -0.525 0.6008
% (Intercept)         -0.1205   0.3891    -0.310 0.7576
% bcat_probes         0.2439    0.2275    1.072  0.2864
% er_probes           0.1383    0.2590    0.534  0.5948
% ifna_probes         -0.4364   0.5056    -0.863 0.3903
% ifng_probes         0.4301    0.5178    0.831  0.4084
% myc_probes          0.2837    0.2330    1.218  0.2264
% pr_probes           0.5789    0.2483    2.331  0.0219   *
% (Intercept)         -0.102321 0.396926  -0.258 0.7972
% bmi                 -0.001038 0.003887  -0.267 0.7900
% bcat_probes         0.252943  0.231140  1.094  0.2767
% er_probes           0.139029  0.260375  0.534  0.5947
% ifna_probes         -0.453502 0.512164  -0.885 0.3782
% ifng_probes         0.449266  0.525393  0.855  0.3947
% myc_probes          0.292758  0.236566  1.238  0.2191
% pr_probes           0.582903  0.250031  2.331  0.0219   *
% (Intercept)         -0.11188  0.38790   -0.288 0.7737
% bmiStatusobese      -0.08019  0.06741   -1.190 0.2373
% bmiStatusoverweight 0.01833   0.07302   0.251  0.8024
% bcat_probes         0.28469   0.23093   1.233  0.2209
% er_probes           0.11686   0.25864   0.452  0.6525
% ifna_probes         -0.60153  0.51434   -1.170 0.2453
% ifng_probes         0.59011   0.52570   1.123  0.2646
% myc_probes          0.31782   0.23483   1.353  0.1793
% pr_probes           0.57227   0.24768   2.311  0.0231   *
% (Intercept)         -0.284628 0.400004  -0.712 0.4786
% bmi                 0.010538  0.006679  1.578  0.1181
% bmiStatusobese      -0.226528 0.114330  -1.981 0.0506   .
% bmiStatusoverweight -0.034711 0.079842  -0.435 0.6648
% bcat_probes         0.280559  0.229061  1.225  0.2239
% er_probes           0.089437  0.257116  0.348  0.7288
% ifna_probes         -0.628292 0.510417  -1.231 0.2216
% ifng_probes         0.590302  0.521401  1.132  0.2606
% myc_probes          0.297308  0.233271  1.275  0.2058
% pr_probes           0.531475  0.247015  2.152  0.0341   *

% [1] "crobsgenes"

% Call:
% lm(formula = as.formula(formula_txt[j]), data = data)

% Coefficients:
%             Estimate Std. Error t value Pr(>|t|)
% (Intercept)         0.456126  0.123888 3.682  0.000381 ***
% bmi                 0.001654  0.004071 0.406  0.685322
% (Intercept)         0.459596  0.054606 8.417  3.7e-13  ***
% bmiStatusobese      0.100893  0.070167 1.438  0.154
% bmiStatusoverweight 0.005772  0.077224 0.075  0.941
% (Intercept)         0.704210  0.163518 4.307  4.04e-05 ***
% bmi                 -0.011059 0.006975 -1.586 0.1162
% bmiStatusobese      0.253491  0.118786 2.134  0.0354   *
% bmiStatusoverweight 0.062836  0.084654 0.742  0.4598
% (Intercept)         1.0667    0.3806   2.803  0.00618  **
% bcat_probes         -0.2284   0.2225   -1.026 0.30740
% er_probes           -0.1481   0.2534   -0.584 0.56041
% ifna_probes         0.4504    0.4945   0.911  0.36477
% ifng_probes         -0.4013   0.5065   -0.792 0.43018
% myc_probes          -0.1402   0.2279   -0.615 0.53986
% pr_probes           -0.6446   0.2429   -2.654 0.00938  **
% (Intercept)         1.014279  0.387058 2.620  0.01029  *
% bmi                 0.003004  0.003791 0.792  0.43014
% bcat_probes         -0.254482 0.225394 -1.129 0.26184
% er_probes           -0.150261 0.253902 -0.592 0.55545
% ifna_probes         0.499868  0.499432 1.001  0.31954
% ifng_probes         -0.456812 0.512332 -0.892 0.37494
% myc_probes          -0.166314 0.230685 -0.721 0.47278
% pr_probes           -0.656157 0.243815 -2.691 0.00847  **
% (Intercept)         1.05662   0.37693  2.803  0.0062   **
% bmiStatusobese      0.11346   0.06550  1.732  0.0867   .
% bmiStatusoverweight 0.01412   0.07095  0.199  0.8427
% bcat_probes         -0.29209  0.22440  -1.302 0.1964
% er_probes           -0.12674  0.25133  -0.504 0.6153
% ifna_probes         0.63723   0.49979  1.275  0.2056
% ifng_probes         -0.58273  0.51083  -1.141 0.2570
% myc_probes          -0.19254  0.22819  -0.844 0.4010
% pr_probes           -0.64072  0.24068  -2.662 0.0092   **
% (Intercept)         1.198471  0.390241 3.071  0.00283  **
% bmi                 -0.008654 0.006516 -1.328 0.18754
% bmiStatusobese      0.233624  0.111539 2.095  0.03905  *
% bmiStatusoverweight 0.057676  0.077893 0.740  0.46097
% bcat_probes         -0.288700 0.223470 -1.292 0.19974
% er_probes           -0.104217 0.250840 -0.415 0.67880
% ifna_probes         0.659208  0.497958 1.324  0.18895
% ifng_probes         -0.582884 0.508675 -1.146 0.25491
% myc_probes          -0.175698 0.227577 -0.772 0.44214
% pr_probes           -0.607216 0.240986 -2.520 0.01353  *

% [1] "fmobsgenes"

% Call:
% lm(formula = as.formula(formula_txt[j]), data = data)

% Coefficients:
%             Estimate Std. Error t value Pr(>|t|)
% (Intercept)         0.436628  0.123787 3.527  0.000643 ***
% bmi                 0.002314  0.004067 0.569  0.570763
% (Intercept)         0.58369   0.05435  10.740 <2e-16   ***
% bmiStatusobese      -0.08452  0.06983  -1.210 0.2291
% bmiStatusoverweight -0.14827  0.07686  -1.929 0.0567   .
% (Intercept)         0.251170  0.160863 1.561  0.12176
% bmi                 0.015034  0.006862 2.191  0.03091  *
% bmiStatusobese      -0.291956 0.116858 -2.498 0.01419  *
% bmiStatusoverweight -0.225840 0.083280 -2.712 0.00794  **
% (Intercept)         0.33317   0.36900  0.903  0.3689
% bcat_probes         -0.13489  0.21576  -0.625 0.5334
% er_probes           0.11973   0.24567  0.487  0.6271
% ifna_probes         -0.56244  0.47947  -1.173 0.2438
% ifng_probes         0.58838   0.49109  1.198  0.2340
% myc_probes          0.41768   0.22093  1.891  0.0618   .
% pr_probes           -0.08815  0.23550  -0.374 0.7090
% (Intercept)         0.291390  0.375705 0.776  0.4400
% bmi                 0.002392  0.003679 0.650  0.5172
% bcat_probes         -0.155669 0.218783 -0.712 0.4786
% er_probes           0.117981  0.246455 0.479  0.6333
% ifna_probes         -0.523056 0.484783 -1.079 0.2835
% ifng_probes         0.544202  0.497304 1.094  0.2767
% myc_probes          0.396892  0.223919 1.772  0.0797   .
% pr_probes           -0.097371 0.236664 -0.411 0.6817
% (Intercept)         0.33459   0.36629  0.913  0.3634
% bmiStatusobese      -0.08029  0.06366  -1.261 0.2104
% bmiStatusoverweight -0.12492  0.06895  -1.812 0.0733   .
% bcat_probes         -0.07254  0.21807  -0.333 0.7402
% er_probes           0.13036   0.24424  0.534  0.5948
% ifna_probes         -0.56035  0.48569  -1.154 0.2517
% ifng_probes         0.58760   0.49642  1.184  0.2397
% myc_probes          0.46651   0.22175  2.104  0.0382   *
% pr_probes           -0.07506  0.23389  -0.321 0.7490
% (Intercept)         0.082260  0.370293 0.222  0.82471
% bmi                 0.015393  0.006183 2.490  0.01464  *
% bmiStatusobese      -0.294047 0.105838 -2.778 0.00666  **
% bmiStatusoverweight -0.202402 0.073911 -2.738 0.00746  **
% bcat_probes         -0.078569 0.212047 -0.371 0.71187
% er_probes           0.090296  0.238018 0.379  0.70532
% ifna_probes         -0.599445 0.472504 -1.269 0.20787
% ifng_probes         0.587878  0.482673 1.218  0.22646
% myc_probes          0.436540  0.215944 2.022  0.04623  *
% pr_probes           -0.134650 0.228668 -0.589 0.55746
